Accelerated Magnetic Resonance Imaging by Adversarial Neural Network

### 2018-01-23 paper.tex
Update acknow

%--------------------- Acknowledgment --------------------%
\subsection{Acknowledgment}
This research is partially supported by the Israel Science Foundation (T.R.R. 1638/16 ) and the IDF Medical Corps (T.R.R.)

>>>>

%--------------------- Acknowledgment --------------------%
\subsection{Acknowledgment}
This study was partially supported by The Israel Science Foundation (1638/16); The Israel Defense Forces (IDF) Medical Corps and Directorate of Defense Research \& Development, Israeli Ministry of Defense (IMOD DDR\&D); The Israeli ministry of science, technology and space (63551).
%This research is partially supported by the Israel Science Foundation (T.R.R. 1638/16 ) and the IDF Medical Corps (T.R.R.)
